Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-16 supp/supp.qmd
Country breakdown

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor)

@@

>>>>

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer)

@@

## What countries use preprints the most?

Unsurprisingly, countries in North America and Europe use preprints more exstensively compared to other countries with countries in Africa, Central America and parts of Asia still slow to use *EcoEvoRxiv* for their preprints (@fig-countries).

```{r, countries}
#| label: fig-countries
#| fig-cap: Percentage of preprints on *EcoEvoRxiv* across countries.

# Create a global map with countried highlighted and shaded according to the frequency of preprints from that country
# First, we need to get the country names and the number of preprints from each country
  countries <- preprints  %>% tabyl(submitting_author_country)  %>% rename("country" = submitting_author_country, "n" = n)  %>% mutate(country = ifelse(country == "NA", "Unknown", country))  %>% arrange(desc(n))  %>% mutate(country=str_to_title(country))

# Now we can plot the map, but before we do we need to make sure the names in the countries file match those in the region of the world map
  world_map <- map_data(map = "world")

# List unique countries
  maps_country_name <- unique(world_map$region) # Names of regions in maps
  countries[!countries$country %in% maps_country_name,] # Names of countries in our data that are not in the maps data, we need to fix these in countries

# Fix names in countries
replace = c("United States Of America" = "USA",  "United Kingdom" = "UK",  "Czechia" = "Czech Republic") 
countries <- countries  %>% mutate(country = str_replace_all(country, replace))

ggplot(countries) +
  geom_map(aes(map_id = country, fill = valid_percent), map = world_map) +
  geom_polygon(data = world_map, aes(x = long, y = lat, group = group), colour = 'black', fill = NA) +
  expand_limits(x = world_map$long, y = world_map$lat) +
  theme_void() +
  coord_fixed() + labs(fill="%")

  p1 <- countries  %>% ggplot(aes(map_id = country)) + geom_map(aes(fill = percent), map = map_data("world"), color = "black") + expand_limits(x = map_data("world")$long, y = map_data("world")$lat) + labs(fill = "Number of preprints", title = "Number of preprints by country") + theme_void() + theme(legend.position = "bottom")
